[dcpo_demsupport]

### 2020-09-29 paper/dcpo_demsupport.Rmd
getting the ns from the point estimations

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

@@

df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result))
})

@@

df_result_clsAPSR <- map(mods, function(aMod){
  tidy(aMod) %>%
    mutate(std.error = vcovHC_se(aMod))
})

@@

df_result_dcpoMeanAPSR <- map(mods, function(aMod){
  aMod %>% 
    tidy %>%
    mutate(std.error = vcovHC_se(aMod))
})

@@

The results are presented in Figure \@ref(fig:visualizeAJPS)

@@

## Models of Effect of Democratic Mood on Institutional Democratization

>>>>

df_result_cls <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = sd.plm)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result),
           n = nobs(result))
})

@@

df_result_dcpoMeanAJPS <- map(ls_mod, function(mod){
  result <- plm(mod, model = "pooling", data = df_dcpoMeanAJPS)
  df_result <- tidy(result) %>%
    mutate(std.error = vcovBK_se(result),
           n = nobs(result))
})

@@

df_result_clsAPSR <- map(mods, function(aMod){
  tidy(aMod) %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod))
})

@@

df_result_dcpoMeanAPSR <- map(mods, function(aMod){
  aMod %>% 
    tidy %>%
    mutate(std.error = vcovHC_se(aMod),
           n = nobs(aMod))
})

@@

The results are presented in Figure \@ref(fig:visualizeAJPS) (and numerically in the Appendix \@ref(replicateAJPS))

@@

## Models of Effect of Democratic Mood on Institutional Democratization {#replicateAJPS}
